QPLIB: A Library of Quadratic Programming Instances

### 2017-02-02 QPLIB-3.tex
proofread website section

The instances of QPLIB are publicly accessible at the website \url{http://qplib.zib.de}.
Scripts and tools developed for MINLPLib 2 \cite{Vigerske2014} were used and extended to create the website.
%
Beyond all instances in GAMS, \texttt{.lp}, and \texttt{.qplib} format, the website provides a rich set of metadata for each
instance: the three letter problem classification (as described in Section \ref{subsec:final set}), basic properties such as the number of variables and constraints of
different types, the sense and convexity/concavity of the objective function, and information on the nonzero structure of the
problem.
%
In addition, we display a visualization of the sparsity patterns of the Jacobian and the Hessian matrix of the
Lagrangian function.  In the plots of the Jacobian nonzero pattern, the linear and nonlinear entries are distinguished
by color.  Figure \ref{fig:sparsitypattern} shows an example for instance QPLIB\_2967.

\begin{figure}
\centering
\includegraphics[scale=0.5]{{QPLIB_2967.jac}.png} \qquad
\includegraphics{{QPLIB_2967.hess}.png}
\caption{Sparsity pattern of Gradient of objective (first line) and Jacobian (left) and of Hessian of Lagrangian function (right) for instance QPLIB\_2967.}
\label{fig:sparsitypattern}
\end{figure}

The entire set of instances can be explored in a searchable and sortable table of selected instance features: problem
classification, convexity of the continuous relaxation, number of (all, binary, integer) variables, (all, quadratic) constraints, nonzeros, hard eigenvalues in $Q^0$, and density of $Q^0$.
%
Finally, a statistics page displays diagrams on the composition of the library according to different criteria: the
number instances according to problem type, variable and constraint types, convexity, number of variables and constraints, and density.
%
A file containing the relevant metadata for each instance can be downloaded in comma-separated-values (\texttt{csv}) format,
so that researchers can easily compile their own subset of instances according to these statistics.

>>>>

The instances of QPLIB are publicly accessible at the website \url{http://qplib.zib.de}, which was created by extending
scripts and tools initially developed for MINLPLib\,2~\cite{Vigerske2014}.
%
Beyond all instances in GAMS, \texttt{.lp}, and \texttt{.qplib} format, the website provides a rich set of metadata for each
instance: the three letter problem classification (as described in Section \ref{subsec:final set}), basic properties such as the number of variables and constraints of
different types, the sense and convexity/concavity of the objective function, and information on the nonzero structure of the
problem.
%
In addition, we display a visualization of the sparsity patterns of the Jacobian and the Hessian matrix of the
Lagrangian function.  In the plots of the Jacobian nonzero pattern, the linear and nonlinear entries are distinguished
by color.  Figure \ref{fig:sparsitypattern} shows an example for instance QPLIB\_2967.

\begin{figure}
\centering
\includegraphics[scale=0.5]{{QPLIB_2967.jac}.png} \qquad
\includegraphics{{QPLIB_2967.hess}.png}
\caption{Example for the sparsity pattern of the Jacobian of the constraint functions (left) and
  of the Hessian of the Lagrangian function (right) for instance QPLIB\_2967.
  The gradient of the objective function is displayed as the first row
  of the Jacobian matrix.}
\label{fig:sparsitypattern}
\end{figure}

The entire set of instances can be explored in a searchable and sortable table of selected instance features: problem
classification, convexity of the continuous relaxation, number of (all, binary, integer) variables, (all, quadratic) constraints, nonzeros, hard eigenvalues in~$Q^0$, and density of~$Q^0$.
%
Finally, a statistics page displays diagrams on the composition of the library according to different criteria: the
number of instances according to problem type, variable and constraint types, convexity, problem size, and density.
%
A file containing the relevant metadata for each instance can be downloaded in comma-separated-values (\texttt{csv}) format,
so that researchers can easily compile their own subset of instances according to these statistics.
